---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  message = FALSE,
  echo = FALSE
)
```

# telecommute

The goal of this repo is to host ideas, data and analysis on telecommuting, its spatial distribution, potential uptake, and benefits.
If the analysis goes well, it could lead to an academic paper on the subject, perhaps with a title like:

> The potential of working from home to tackle loneliness, air pollution and climate change: a geographical approach

Target journal:

josis

## Introduction

- Previous work on telecommuting
- Hypotheses
- Policy relevance

## Data and methods

The main dataset for the study was the 2011 Census for England and Wales on mode of transport to work.
Mainly from home (MFH) is a category of travel to work (TTW), alongside other modes.
Over the last few decades, the proportion of people who word from home has been increasing, according to this measure, as illustrated in the Figure 
1.
<!-- \ref(fig:historic). -->

```{r historic, fig.cap="Proportion of trips by main mode"}
modes_historic = read_csv("modes.csv")
modes_historic$year = as.character(modes_historic$year)
g = ggplot(modes_historic, aes(mode, proportion, fill = year)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  scale_color_brewer(type = "seq") +
  theme(axis.text.x = element_text(angle = 45))
g
```
